Clustering time series based on probability distributions across temporal granularities

### 2021-11-17 main.Rmd
language in application section

Clustering of the $24$ prototypes <!--and the data subset consisting of $353$ customers--> was conducted with all three distances, JS-NQT, JS-RS and WPD, and is summarised in Figures \ref{fig:opt-cluster-tsne-jsd}, \ref{fig:hod-ind-group-png} and \ref{fig:parcoord-application}. In the following plots, the median is shown by a line, and the shaded region shows the area between the  $25^{th}$ and $75^{th}$ percentiles.<!--All customers with the same color represent the same clustered groups. --> Groups are colored differently whenever they represent different groupings. While plotting the clusters, RS-based scaling is applied to each customer, so that no customer dominates the shape of the summarized clusters because of magnitude. The plotting scales are not displayed since we want to emphasize comparable patterns rather than scales. The idea is that a customer in a cluster may have low total energy usage, but their behavior may be quite similar to a customer with high usage with respect to distributional pattern or significance across cyclic granularities.

>>>>

Clustering of the $24$ prototypes <!--and the data subset consisting of $353$ customers--> was conducted with all three distances, JS-NQT, JS-RS and WPD, and is summarised in Figures \ref{fig:opt-cluster-tsne-jsd}, and \ref{fig:parcoord-application}. In the following plots, the median is shown by a line, and the shaded region shows the area between the  $25^{th}$ and $75^{th}$ percentiles.<!--All customers with the same color represent the same clustered groups. --> Groups are colored differently whenever they represent different groupings. While plotting the clusters, RS-based scaling is applied to each customer, so that no customer dominates the shape of the summarized clusters because of magnitude. The plotting scales are not displayed since we want to emphasize comparable patterns rather than scales. The idea is that a customer in a cluster may have low total energy usage, but their behavior may be quite similar to a customer with high usage with respect to distributional pattern or significance across cyclic granularities.
